---
title: "Regression Analysis for Open Pipeline & Revenue"
output: html_document
author: Hilary Lai
date: 2020-08-06
---

```{r data, include=FALSE}
library(readr)
library(tidyverse)
library(knitr)
options(digits=2)
options(scipen = 1)

open.pav <- read_csv("open_pav_by_mth.csv")
rev <- read_csv("rev_by_mth.csv") %>%
  filter(!(Director %in% c("Zhao, Thomas", "ZZZZ"))) 

#consolidate open pav
open.pav <- open.pav %>%
  group_by_at(names(.)[1:5]) %>%
  dplyr::summarise(PAV = sum(`Peak Annual Value Calc`)) %>%
  ungroup

open.pav <- open.pav %>% 
  separate(Snapshot_Month, c("Month", "Year"), sep = " ")

open.pav <- open.pav %>%
  mutate(Month = case_when(
    open.pav$Month == "January" ~ 1,
    open.pav$Month == "February" ~ 2,
    open.pav$Month == "March" ~ 3,
    open.pav$Month == "April" ~ 4,
    open.pav$Month == "May" ~ 5,
    open.pav$Month == "June" ~ 6,
    open.pav$Month == "July" ~ 7,
    open.pav$Month == "August" ~ 8,
    open.pav$Month == "September" ~ 9,
    open.pav$Month == "October" ~ 10,
    open.pav$Month == "November" ~ 11,
    open.pav$Month == "December" ~ 12,
  ))

open.pav <- open.pav %>%
  mutate(Snapshot_mth = as.numeric(Year)*100 + as.numeric(Month)) %>%
  .[,c(8,1:3,6:7)]

open.pav <- open.pav %>%
  mutate(adj_mth = Snapshot_mth + 100) %>%
  .[,-1]
  
rev <- rev %>% 
  mutate(Region = case_when(
    rev$Region == "Asean" ~ "AS",
    rev$Region == "Australia" ~ "AL",
    rev$Region == "India" ~ "IN",
    rev$Region == "Korea" ~ "KR",
    rev$Region == "Taiwan" ~ "TA"),
  Director = case_when(
    rev$Director == "Hong, SK" ~ "SHONG",
    rev$Director == "Hsu, Eric" ~ "EHSU2",
    rev$Director == "JD Kang" ~ "JKANG2",
    rev$Director == "Ted Park" ~ "TPARK",
    rev$Director == "Wan, Daryl" ~ "MWAN"))

#fix revenue format
rev$Revenue <- gsub("[(]", "-", rev$Revenue)
rev$Revenue <- gsub("[),$]", "", rev$Revenue)

#align column names
names(open.pav)[1:2] <- c("End_Mkt_Segment", "BU")

dat <- full_join(rev, open.pav, by = c("Fiscal_Mth" = "adj_mth", "Region" = "Region", "Director" = "Director", "BU" = "BU", "End_Mkt_Segment")) 
dat[is.na(dat)] <- 0
dat$Revenue <- as.numeric(dat$Revenue)
library(readr)
library(tidyverse)

open.pav <- read_csv("open_pav_by_mth.csv")
rev <- read_csv("rev_by_mth.csv") %>%
  filter(!(Director %in% c("Zhao, Thomas", "ZZZZ"))) 

#consolidate open pav
open.pav <- open.pav %>%
  group_by_at(names(.)[1:5]) %>%
  dplyr::summarise(PAV = sum(`Peak Annual Value Calc`)) %>%
  ungroup

open.pav <- open.pav %>% 
  separate(Snapshot_Month, c("Month", "Year"), sep = " ")

open.pav <- open.pav %>%
  mutate(Month = case_when(
    open.pav$Month == "January" ~ 1,
    open.pav$Month == "February" ~ 2,
    open.pav$Month == "March" ~ 3,
    open.pav$Month == "April" ~ 4,
    open.pav$Month == "May" ~ 5,
    open.pav$Month == "June" ~ 6,
    open.pav$Month == "July" ~ 7,
    open.pav$Month == "August" ~ 8,
    open.pav$Month == "September" ~ 9,
    open.pav$Month == "October" ~ 10,
    open.pav$Month == "November" ~ 11,
    open.pav$Month == "December" ~ 12,
  ))

open.pav <- open.pav %>%
  mutate(Snapshot_mth = as.numeric(Year)*100 + as.numeric(Month)) %>%
  .[,c(8,1:3,6:7)]

open.pav <- open.pav %>%
  mutate(adj_mth = Snapshot_mth + 100) %>%
  .[,-1]
  
rev <- rev %>% 
  mutate(Region = case_when(
    rev$Region == "Asean" ~ "AS",
    rev$Region == "Australia" ~ "AL",
    rev$Region == "India" ~ "IN",
    rev$Region == "Korea" ~ "KR",
    rev$Region == "Taiwan" ~ "TA"),
  Director = case_when(
    rev$Director == "Hong, SK" ~ "SHONG",
    rev$Director == "Hsu, Eric" ~ "EHSU2",
    rev$Director == "JD Kang" ~ "JKANG2",
    rev$Director == "Ted Park" ~ "TPARK",
    rev$Director == "Wan, Daryl" ~ "MWAN"))

#fix revenue format
rev$Revenue <- gsub("[(]", "-", rev$Revenue)
rev$Revenue <- gsub("[),$]", "", rev$Revenue)

#align column names
names(open.pav)[1:2] <- c("End_Mkt_Segment", "BU")

dat <- full_join(rev, open.pav, by = c("Fiscal_Mth" = "adj_mth", "Region" = "Region", "Director" = "Director", "BU" = "BU", "End_Mkt_Segment")) 
dat[is.na(dat)] <- 0
dat$Revenue <- as.numeric(dat$Revenue)
dat <- dat %>%
  filter(PAV>0, Revenue>0)
aeg <- dat %>%
  filter(End_Mkt_Segment == "AEG")
```
# Dataset

The dataset I use combines each year's snapshot of the **Peak Annual Value (PAV)** for open pipeline, with each year's **revenue value**.

For each open pipeline snapshot, the time is adjusted to 1 year ahead to be compared with revenue. For example, the PAV column of 2020 March is actually a snapshot of 2019 March.

The dataset contains the following fields:

* Fiscal month
* BU
* Region
* Director
* PAV
* Revenue

A partial look of part of the dataset:

```{r table, echo=F}
library(knitr)
kable(head(dat))
```

# ANOVA (Analysis of Variance) with all Variables

Next, I run an ANOVA analysis with $Revenue^{(0.01)}$ as the dependent variable, and $ln{(PAV)}$, BU, Region, and End Customer Segment as independent variables. The goal is to see whether there are differences in the means of Revenue value between each variable.

*Note:*

*1. I did not use Director as one of the independent variables, because it is highly correlated with Region and redundant for ANOVA.*

*2. To keep all values positive for transformation, I only included data with PAV & Revenue >0. The purpose of keeping all values positive is to keep the distribution normal.*

*3. The 0.1 comes from Box-Cox Transformation of data. The purpose is to make data normal in order to meet the requirements for linear regression analysis. We will use this value from now on.*

```{r anova, echo=F, include=F}

library(ggplot2)
library(car)
library(gridExtra)

model <- lm(Revenue ~ log(PAV), dat)
bc <- boxCox(model)
lamb <- round(bc$x[which.max(bc$y)],2)

#lm with all dat
dat.fit <- lm(Revenue^lamb ~ log(PAV) +
     BU+
     Region+
       End_Mkt_Segment, dat)

```

## Results:

```{r anova.show, echo=F, include=T}
summary.aov(dat.fit)
```

As shown, all 4 variables have significant F values (p-vale < 0.01). Therefore, we can say that **there is enough evidence that the means of $(Revenue)^{(0.1)}$ differ between each category.**

# Linear Regression Model for Each Variable

Next, I run linear regression analysis for each variable from each director and segment.

The linaer model should look something like this:

### $(Revenue)^{(0.1)}$ = `r "$\\beta_0$"` + `r "$\\beta_1$"` * $\ln(PAV)$ + `r "$\\epsilon$"`

*Note: `r "$\\epsilon$"` = Error variable, `r "$\\beta_0$"` = intercept.*

## Director

```{r director, echo=F, include=F}

#dir = eric
dat.eric <- lm((Revenue)^lamb~ 
              log(PAV),  dat %>%
                filter(Director == "EHSU2"))
#dir = mwan
dat.mwan <- lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(Director == "MWAN"))

#dir = shong
dat.shong <- lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(Director == "SHONG"))

#dir = TPARK
dat.tpark <- lm((Revenue)^lamb~ 
                  log(PAV), dat %>%
                  filter(Director == "TPARK"))
```

For each director, I get a linear regression model:

### 1. Eric Hsu

```{r dat.eric, echo=F, include=T}
summary(dat.eric)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Director = Eric,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.eric$coefficients[1]` + `r dat.eric$coefficients[2]` * $\ln(PAV)$.**

### 2. Daryl Wan

```{r reg.mwan, echo=F, include=T}
summary(dat.mwan)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Director = Daryl,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.mwan$coefficients[1]` + `r dat.mwan$coefficients[2]` * $\ln(PAV)$.**

### 3. SK Hong

```{r reg.shong, echo=F, include=T}
summary(dat.shong)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Director = SK,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.shong$coefficients[1]` + `r dat.shong$coefficients[2]` * $\ln(PAV)$.**

### 4. Ted Park

```{r reg.tpark, echo=F, include=T}
summary(dat.tpark)
```


As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Director = Ted,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.tpark$coefficients[1]` + `r dat.tpark$coefficients[2]` * $\ln(PAV)$.**

## Segment

```{r seg, echo=F, include=F}
#AEG
dat.AEG  <- lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(End_Mkt_Segment == "AEG"))

#ASD
dat.ASD <-lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(End_Mkt_Segment == "ASD"))


#AUT
dat.AUT <-lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(End_Mkt_Segment == "AUT"))


#COM
dat.COM <-lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(End_Mkt_Segment == "COM"))


#CON
dat.CON <-lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(End_Mkt_Segment == "CON"))

#DHC
dat.DHC <-lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(End_Mkt_Segment == "DHC"))

#INS
dat.INS <-lm((Revenue)^lamb~ 
                 log(PAV), dat %>%
                 filter(End_Mkt_Segment == "INS"))
```

For each segment, I get a linear regression model:

### 1. AEG
```{r dat.AEG, echo=F, include=T}
summary(dat.AEG)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Region = AL,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.AEG$coefficients[1]` + `r dat.AEG$coefficients[2]` * $\ln(PAV)$.**

### 2. ASD
```{r dat.ASD, echo=F, include=T}
summary(dat.ASD)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Region = AS,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.ASD$coefficients[1]` + `r dat.ASD$coefficients[2]` * $\ln(PAV)$.**

### 3. AUT
```{r dat.AUT, echo=F, include=T}
summary(dat.AUT)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Region = IN,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.AUT$coefficients[1]` + `r dat.AUT$coefficients[2]` * $\ln(PAV)$.**

### 4. COM
```{r dat.COM, echo=F, include=T}
summary(dat.COM)
```


As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Region = KR,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.COM$coefficients[1]` + `r dat.COM$coefficients[2]` * $\ln(PAV)$.**

### 5. CON

```{r dat.ta, echo=F, include=T}
summary(dat.CON)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Region = TA,  $(Revenue)^{(0.1)}$ and $\ln(PAV+1)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.CON$coefficients[1]` + `r dat.CON$coefficients[2]` * $\ln(PAV)$.**

### 6. DHC

```{r dat.DHC, echo=F, include=T}
summary(dat.DHC)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Region = TA,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.DHC$coefficients[1]` + `r dat.DHC$coefficients[2]` * $\ln(PAV)$.**

### 7. INS

```{r dat.INS, echo=F, include=T}
summary(dat.INS)
```

As shown, small p-value (<0.01) indicates that we can reject the null hypothesis, and conclude that there is strong evidence to show that for Region = TA,  $(Revenue)^{(0.1)}$ and $\ln(PAV)$ are linearly related.

The model:

**$(Revenue)^{(0.1)}$ = `r dat.INS$coefficients[1]` + `r dat.INS$coefficients[2]` * $\ln(PAV)$.**

# Summary

We generated several models using differenct slices of data.

Note that for directors , the $R^2$ value is relatively high, (Especially, Eric, SK, and Ted all have $R^2$ over 50%). This means that **a high percentage of data can be explained by the model.** As for End Market Segment,  AEG, AUT, and INS all have $R^2$ over 0.5, which means that their models are also a good indicator. Even for the lowest segment "CON"'s model, over 20% of data can be explained.

To summarize in a plot, it will look like this:

### By Director

```{r plot.dir, echo=F, include=T}

#plot by director
plot.dir <- dat %>%
  ggplot(aes(x = log(PAV), y = (Revenue)^lamb, color = Director)) +
  geom_point(size = 0.3) +
  xlab("ln(PAV)")+
  ylab("Revenue^(0.1)")+
  ggtitle("Regression Plot by Director") +
  stat_smooth(method = "lm", aes(fill = Director), se=FALSE, fullrange=TRUE)
plot.dir
```

### By Segment

```{r plot.reg, echo=F, include=T}

#plot by segment
plot.reg <- dat %>%
  ggplot(aes(x = log(PAV+1), y = (Revenue)^lamb, color = End_Mkt_Segment)) +
  geom_point(size = 0.3) +
   xlab("ln(PAV)")+
  ylab("Revenue^(0.1)")+
    ggtitle("Regression Plot by Segment") +
  stat_smooth(method = "lm", aes(fill = End_Mkt_Segment), se=FALSE, fullrange=TRUE)
plot.reg
```

# Forecast and Predictions

To use the models as forecast, we can apply some examples:

## 1. Example A: 

#### At March 2019, open pipeline for Eric as director, Taiwan as region, and AEG as segment has a total PAV value of $15,000.

To calculate the revenue, we can apply the model formulas:

By director: **$(Revenue)^{(0.1)}$ = `r dat.eric$coefficients[1]` + `r dat.eric$coefficients[2]` * $\ln(15000)$.**

We can get that the Revenue forecast for March 2020 in this case $202.

## 1. Example B: 

#### At April 2018, open pipeline for SK as director, KR as region, and COM as segment has a total PAV value of $60,000.

By segment:  **$(Revenue)^{(0.1)}$ = `r dat.COM$coefficients[1]` + `r dat.COM$coefficients[2]` * $\ln(60000)$.**

We can expect that the revenue for April 2019 would be $4,143.
